POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2023-07-10 challenges.tex
Change the order of challenges.
Comment out notes in challenges.

\paragraph{Notes about this challenge}
Strong barbed bisimilarity is interesting by itself for this challenge, but the proof that it is an equivalence relation does not require up-to techniques, which are wide spread and interesting.
The definition of strong barbed congruence requires introducing contexts, but this is actually nice, since they are so prevalent in the field and we want to cover as many basics as possible.
The theorem about the strong barbed congruence requires up-to techniques, but also seems to involve introducing a structural equivalence, which is possibly not desirable.
On the other hand, it is a nice application of structural congruence which does not ``ruin'' the semantics.

>>>>

%\paragraph{Notes about this challenge}
%Strong barbed bisimilarity is interesting by itself for this challenge, but the proof that it is an equivalence relation does not require up-to techniques, which are wide spread and interesting.
%The definition of strong barbed congruence requires introducing contexts, but this is actually nice, since they are so prevalent in the field and we want to cover as many basics as possible.
%The theorem about the strong barbed congruence requires up-to techniques, but also seems to involve introducing a structural equivalence, which is possibly not desirable.
%On the other hand, it is a nice application of structural congruence which does not ``ruin'' the semantics.
